\PaperTitle

### 2024-05-05 Final_Report/paper.tex
added log reg

  A thorough evaluation of the models was conducted through testing and validation sets, hyperparameter optimization employing cross-validation and grid search, and computing accuracy and Macro F1 scores. The results showed that the Neural Network model 
  achieved the highest accuracy of $85\%$ and Macro F1 score of 84.

@@

Variables $w_i$ and $b$ correspond to weight and bias, respectively. Both of these terms get set by the training process of the model, which we'll discuss shortly. 
The resulting value, $z$, is the input to an {\it activation function}, which, depending on which is used, modifies and normalizes the output before it is passed to the next node.

@@

These metrics are applicable to all models and allow for
a direct comparison for each of their performances. Two other metrics: precision and recall, help to provide a more detailed understanding of the model's performance on a class-to-class basis.
\newline \\
The equation for \textbf{Accuracy}: \\
\[
Accuracy= \frac{TP + TN}{TS}
\]
\newline \\
The equation for \textbf{Macro F1}: \\
\[
Macro F 1= \frac{1}{n} \sum_{1}^{n} \frac{2*Precision_i*Recall_i}{Precision_i+Recall_i}
\]
\newline \\
The equation for \textbf{Recall}: \\
\[
Recall= \frac{TP}{TP + FN}
\]
\newline \\
The equation for \textbf{Precision}: \\
\[
Accuracy= \frac{TP}{TP + FP}
\]
\\
Accuracy is the score that rates the effectiveness of a model at classification overall (ie. how many it predicted correctly out of the total set).

Macro F1 is the harmonic average of the of precision and recall for every class, and then taking the average of these calculated scores across all classes.

Recall is the calculation of how many the model correctly classified within a class (ie. how many truly belong in that class in the entire dataset). 
Precision is the calculation of how many the model correctly classified within a class (ie. can be thought of as class accuracy).

@@

\begin{table}[!h]
  \begin{center}
  \caption{Accuracy and Macro F1 Scores for Each Model}
  \label{tab:results}
  \begin{tabular}{|c|c|c|}
    \hline
    Model & Accuracy & Macro F1 \\
    \hline
    Logistic Regression & 56\% & 0.00 \\
    K-Nearest Neighbors & 77\% & 0.00 \\
    Random Forest & 83\% & 82\% \\
    Neural Network & 85\% & 84\% \\
    \hline
  \end{tabular}
  \end{center}
\end{table}

>>>>

  A thorough evaluation of the models was conducted through testing and validation sets, hyperparameter optimization employing cross-validation and grid search, and computing accuracy and Macro F1 scores. The results showed that the Neural Network model 
  acheived the highest accuracy of $85\%$ and Macro F1 score of 84.

@@

Variables $w_i$ and $b$ correspond to weight and bias, respectivly. Both of these terms get set by the training process of the model, which we'll discuss shortly. 
The resulting value, $z$, is the input to an {\it activation function}, which, depending on which is used, modifies and normalizes the output before it is passed to the next node.

@@

These metrics are applicable to all models and allow for
a direct comparison for each of their performances. Two other metrics: precision and recall, help to provide a more detailed understanding of the model's performance on a class-to-class basis.
\newline \\
The equation for \textbf{Accuracy}: \\
\[
Accuracy= \frac{TP + TN}{TS}
\]
\newline \\
The equation for \textbf{Macro F1}: \\
\[
Macro F 1= \frac{1}{n} \sum_{1}^{n} \frac{2*Precision_i*Recall_i}{Precision_i+Recall_i}
\]
\newline \\
The equation for \textbf{Recall}: \\
\[
Recall= \frac{TP}{TP + FN}
\]
\newline \\
The equation for \textbf{Precision}: \\
\[
Accuracy= \frac{TP}{TP + FP}
\]
\\
Accuracy straightforwardly measures the probability of correctly identifying a packet based on the rate at which packets are correctly classified in the validation or test sets.

Macro F1 is more opaque in terms of being intuitively understood, but it's a harmonic average of each class's metrics of precision and recall, averaged across all classes

Recall is the calculation of how many classifications the model got correct for a given class, out of the total number of packets truly from that class.

Precision is the calculation of how many classifications that were marked as as class truly belong to each class.

@@

\begin{table}[!h]
  \begin{center}
  \caption{Accuracy and Macro F1 Scores for Each Model}
  \label{tab:results}
  \begin{tabular}{|c|c|c|}
    \hline
    Model & Accuracy & Macro F1 \\
    \hline
    Logistic Regression & 56\% & 0.00 \\
    K-Nearest Neighbors & 77\% & 75\% \\
    Random Forest & 83\% & 82\% \\
    Neural Network & 85\% & 84\% \\
    \hline
  \end{tabular}
  \end{center}
\end{table}
